\subsection{Les rêves eugéniques de Ambrose Morgens}

\paragraph{} Le sorcier \gls{ams} souhaite utiliser la progéniture encore \emph{très fraîche} de 
\gls{clg} pour ses expériences de création de raçe supérieur.

\subsection{L'Ordre Esotérique de Dagon de Throg's Neck}

\paragraph{} Au début des années 1930, \gls{ams} est rentrée en contact avec quelque uns des membres
de l'\gls{osd}, et a commencé avec eux un avantageux commerce. En échange des services de la secte, 
le sorcier leur fournit, sur une base régulière, des \emph{femelles} - comprendre des femmes qu'il a 
kidnappées pour ses propres besoins. Une fois ces dernières rescapés du laboratoire de son comparse, et 
créature, \gls{evk}.

\subsection{Le crime}

 At 8:00 pm on March 1, 1932, the nurse-maid, \gls{bgw}, put 20-month-old Charles Lindbergh, Jr., in his crib. 
She then proceeded to pin the blanket covering him with two large safety pins so as to prevent it from moving while he slept.
At around 9:30 p.m., Col. Lindbergh heard a noise that made him think some slats had fallen off an orange crate in the kitchen. 
At 10:00 p.m., Gow discovered that the baby was missing from his crib. She in turn went to ask Mrs. Lindbergh, who was just coming
 out of the bath, if she had the baby with her. After not finding Charles Lindbergh, Jr., with his mother, 
the nurse-maid then proceeded down stairs to speak with Lindbergh, who was in the library/study just beneath the baby's nursery room 
in the southeast corner of the house. Charles Lindbergh then proceeded up to the nursery to see for himself that his son was not in his crib. 
While surveying the room, he discovered a white envelope had been left on the radiator that formed the window sill. Lindbergh 
proceeded to locate his Springfield rifle and search the rest of the house looking for intruders. Within 30 minutes, the local 
police were on route to the house, as were the media and Lindbergh's attorney. There was a single distinguished footprint and 
indentations discovered a short time later just below the window in the mud due to the rainy and blustery conditions that day 
and into the evening. After the authorities arrived on the scene and began to search the immediate area surrounding the house,s
 a short distance away in a cluster of bushes were found three sections of a smartly designed but rather crude-looking ladder.

http://en.wikipedia.org/wiki/Evalyn\_Walsh\_McLean

http://en.wikipedia.org/wiki/Gaston\_Means

http://www.charleslindbergh.com/

% http://news.google.com/newspapers?id=cXAbAAAAIBAJ&sjid=WEsEAAAAIBAJ&dq=gaston%20means&pg=3047%2C5884625
% http://news.google.com/newspapers?id=cXAbAAAAIBAJ\&sjid=WEsEAAAAIBAJ\&dq=gaston\%20means&pg=3047\%2C5884625

% http://en.wikipedia.org/wiki/Saint_Raymond's_Cemetery,_Bronx

% http://en.wikipedia.org/wiki/Virginia_Hall

% http://www.flickr.com/photos/neatnessdotcom/1564083369/sizes/l/